On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-09 docs/mvfits_paper/mvf.tex
Mixing Talor series argument with Generalised Stone-Weierstrass Theorem

The study of continuous scalar functions often centers about their expansion in terms of monomials.

@@

From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $K(N+1)$. This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.

@@

given training data thought to be related to a continuous multivariate function, it may, particularly on small scales, be well approximated by a polynomial in an appropriate coordinate basis.

>>>>

The study of continuous scalar functions often centers about their Taylor series expansion.

@@

From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion).

@@

Formally, the applicability of the truncated expansion over a local region is made rigorous by the Generalised Stone-Weierstrass Theorem \cite{Hassani:2013}.
\par These ideas are key to the perspective of \gmvp{}:
given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.
